The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

V86   How important are adventure and taking risks to the person surveyed?
V119 How good is competition?

@@

V65   I seek to be myself rather than to follow others
V66   I live up to what my friends expect
V67   I decide my goals in life by myself
V78   How good / bad is greater respect for authority to the person surveyed?
V186 How often do you attend religious services?
V198 How justifiable can claiming government benefits be?
V199 How justifiable can avoiding a fare on public transport be?
V200 How justifiable can cheating on taxes be?

>>>>

V86   How important are adventure and taking risks to the person surveyed?

V119 How good is competition?

@@

V65   I seek to be myself rather than to follow others

V66   I live up to what my friends expect

V67   I decide my goals in life by myself

V78   How good / bad is greater respect for authority to the person surveyed?

V186 How often do you attend religious services?

V198 How justifiable can claiming government benefits be?

V199 How justifiable can avoiding a fare on public transport be?

V200 How justifiable can cheating on taxes be?
